---
title: "AIDs Drug Tests"
author: "Rachelle Galindo"
date: "May 4, 2019"
output: 
  html_document:
    number_section: true
    toc: true
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
avast <-read.csv(file="avastivironal.csv",header=TRUE)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!--> 

A new  preventative aides (abacavirinol) is under test in clinical trials to keep AIDs from occuring so now we want to know whether or not the vaccine wil be effective to patients across the board and consider how the vaccine will effect in different subgroups. 

By doing this we will give a placebo and 



The first question is this: Does abacarvirinol have any affect on whether one contracts AIDS or not?

$H_0:$ Abacavirnol has no effect on whether one contracts AIDS or not

$H_1:$ Abacavirinol has an effect on whether one contacts AIDS or not

The remaining questions are: Does abacavirinol have a different effect base on gender 

$H_0:$ Gender has no effect on whether abacavirinol offers any protection against contracting AIDS

$H_1:$ Gender has an affect on whether abacavirinol offers any protection against contracting AIDS

The remaining questions are: Does IV drug use make an affect/ difference in vaccine effectiveness?

$H_0:$ IV drug use has no effect on vaccine effectiveness

$H_1:$ IV drug use has an effect on vaccine effectiveness

The remaining last question: Does sexual oreintation make a difference in vaccine effectiveness?

$H_0:$ Sexual oreintation has no effect on vaccine effectivenss

$H_1:$ Sexual oreintation has an effect on vaccine effectiveness

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

For each hypothesis test the graphical summary will be a bar plot, the numerical summary will be a cross tabulation, and a chi-squared test will be used for the inferential results.

#Results General Effectiveness
Is the vaccine effective in general population?
<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->


## Descriptive Results

Here is the bar plot, numerical summary, and chi-squared test results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->
```{r}
barchartGC(~infected+treatment, data=avast, type='percent')
```
The bar chart shows that the vaccine did have some effect.The incidence of aids is smaller than who got the vaccine than the ones who didn't.


### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
xtabs(~infected+treatment, data=avast)
```
The numerical results shows that there's is a higher result for the people who have aids that took the placebo than the people who have aids that didn't take the placebo. For the people who don't have aids, the whos who took the placebo didn't   


## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
```{r}
chisqtestGC(~infected+treatment, data=avast)
```


#Results Gender Effectiveness 
Does gender have an effect?
<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->


## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(~infected+sex, data=avast, type='percent')
```



### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
xtabs(~infected+sex, data=avast)
```

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisqtestGC(~infected+sex, data=avast)
```

#Results IV Drug Use effectiveness 
Does the IV drug use make a difference in vaccine effectiveness?
<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->


## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(~infected+Ivdrug, data=avast, type='percent')
```


### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
xtabs(~infected+Ivdrug, data=avast)
```

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisqtestGC(~infected+Ivdrug, data=avast)
```

#Results Sexual Orientation effectiveness
Does sexual oreintation make a difference in vaccine effectiveness?
<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->


## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(~infected+LBGT, data=avast, type='percent')
```


### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
xtabs(~infected+LBGT, data=avast)
```

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisqtestGC(~infected+LBGT, data=avast)
```

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

